A Domain-Driven, Generative Data Model for BigPetStore

### 2014-10-12 bdcloud_paper/latex/paper.tex
Added discussion of Java implementation.

The current implementation was prototyped in Python.  We are working to implement the model using Hadoop and Spark.  We will commit the resulting implementations to BigPetStore hosted in the Apache BigTop distribution to enable ease of access and immediate benefit to current users.

>>>>

The current implementation was prototyped in Python.  We are finishing a Java implementation that can be used from the command-line, Hadoop, and Spark, enabling massive parallelization and improved scaling.  As part of the effort to re-write the framework in Java, we are abstracting classes for statistical modeling and simulation for reuse in developing data generators for other domains. We will commit the resulting implementation to BigPetStore hosted in the Apache BigTop distribution to enable ease of access and immediate benefit to current users.
